How to Avoid OOTA Without Really Trying

### 2024-10-06 paper/ootavacuous.tex
ootavacuous: Section 7.4 suggest less-surprising optimization
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

However, a per-thread analysis compiler can translate this into the
machine-code equivalent of:
\begin{quote}
\begin{verbatim}
int r1 = (x != 0);
int r2;
int r3 = (x != 0);
int r4 = (y != 0);
if (r1 != r3) {
   r2 = r4;
   z = 1;
} else {
   r2 = r1;
   z = (r2 == r4);
}
\end{verbatim}
\end{quote}
In effect, the \co{r2} load is merged with the \co{r1} load in
executions where \co{r1} is equal to \co{r3} or to \co{r4}, and it is
merged with the \co{r3} load in other executions.

>>>>

Although one would expect an optimizing compiler to discard the unused
loads into \co{r1} and \co{r3}, one could imagine a perverse compiler
instead using per-thread analysis to translate this into the machine-code
equivalent of:
\begin{quote}
\begin{verbatim}
int r1 = (x != 0);
int r2;
int r3 = (x != 0);
int r4 = (y != 0);
if (r1 != r3) {
   r2 = r4;
   z = 1;
} else {
   r2 = r1;
   z = (r2 == r4);
}
\end{verbatim}
\end{quote}
In effect, the \co{r2} load is merged with the \co{r1} load in
executions where \co{r1} is equal to \co{r3} or to \co{r4}, and it is
merged with the \co{r3} load in other executions.
